---
title: "Alcohol vs Seat choice"
author: "Larissa Vera"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

## Method
I predict alcohol consumption based on where you sit

$H_0$: There is no difference between the average number of drinks consumed
between people conditioned on the row they sit in.

$H_A$: There is a difference between the average number of drinks consumed
between people conditioned on the row they sit in.


alcohol is numerical 
seat is categorical 
so we used helper file num~ cat 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The boxlpot shows that one who sits in the back is affected the most by the numberof drinks they've had.

  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

the box plot shows drunks are mostly in the back seat. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

the average of those who seat in the back is 8.55. While the mean for those who sit in the front is 1.78 and the mean for the back is 3.33. Showing those who sit in the back row has had more drinks. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

P value is 0.0001166 which is lower than 0.05. Therefore we reject the null hypothesis. 

```{r}
plot(TukeyHSD(model1))
```

Tukey shows that middle-front have no difference. The middle back and front back show that there is a difference due to 0 not being in the interval like midel- front is.

## Conclusions

In conclusion there is a difference between the average number of drinks consumed and the row you sit. So the null hypothesis is rejected since the P value is 0.000116 which is less than 0.05. 

