---
title: "Alcohol vs Seat choice"
author: "Larissa Vera"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

## Method
I predict alcohol consumption based on where you sit

$H_0$: There is no difference between the average number of drinks imbibed
between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

alcohol is numerical 
seat is categorical so we used helper file num~ cat 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

the box plot shows drunks are mostly in the back seat. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

the average of those who seat in the back 55 is higher than the ones seated in the front 20

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

P value is 0.000116 which is lower than 0.05 so we reject the null hypothesis

## Conclusions


